Supporting Information: High resolution, annual maps of the characteristics of smallholder-dominated croplands at national scales

### 2021-03-07 inst/manuscript/si.Rmd
Edits to ms and si, plus commit of many si figures

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: false
spacing: doublespacing
# abstract: The abstract can go either here or below
keywords: rmarkdown, reproducible science
bibliography: 
  - references.bib
  - knitcitations.bib
csl: ecology.csl

@@

Where $\beta_{0-5}$ are the weights assigned to each accuracy metric that sum to 1. For the current production version, $\beta_{0-5}$ were assigned as 0.4, 0.2, 0.2, 0.1, and 0.1.

@@

Where $\theta$ represents the true cover type of a pixel (field or not field), *D* is the worker's label of that field, and *W$_i$* is an individual worker.  Looking in greater details at this equation, the first half of the righthand side of the equation, P(W$_i$|D), is the "prior" for worker *i* for the current site based on their history of scores from accuracy assessment assignments. The second term, P($\theta$|D, W$_i$), is the probability that the actual class of the pixel in the current assignment is the class that worker *i*'s says that it is, which is either 0 or 1. There are four possible values for this second term:

@@

Equations \ref{eq:pacc1} and \ref{eq:pacc2} are producer's accuracies, thus the maximum worker likelihood is equivalent to the worker's average producer's accuracy.

@@

The other component of equation \ref{eq:prior}, P(W$_i$), is the worker's average score over *m* accuracy assessment assignment:  
\begin{equation} 
\mathrm{P(W_i) \propto \frac{1}{m}\sum_{j=1}^{m}score_j}
\end{equation}

Thus equation \ref{eq:prior} uses two measures of worker accuracy, 1) their overall average accuracy score multipled by 2) their average producer's accuracy to create a *weight* for their individual maps for the given site. Equation \ref{eq:main} becomes:

@@

\clearpage
$$
Weight_A = score_A * PA_A(field) = P(W_A)P(D=field|W_A) = `r sc[1, 2]` * `r sc[1, 4]` = `r wtA`
$$

@@

```{r labelriskhist, echo = FALSE, out.width="45%", fig.cap="The distribution of Bayesian Risk values for training (left column) and validation (right column) sites in each AOI, with the average value indicated by vertical lines. The first three rows (panel titles beginning with 'Cl') indicate distributions of Bayes Risk in the initial training clusters, including the first ('Cl2a') and second ('Cl2b') mappings of Cluster 2.", fig.align='center', message=FALSE, results='hold'}
knitr::include_graphics('figures/si_label_risk_hists.png')
```

>>>>

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: yes
spacing: doublespacing
# abstract: The abstract can go either here or below
keywords: rmarkdown, reproducible science
bibliography: 
  - references.bib
  - knitcitations.bib
csl: ecology.csl

@@

Where $\beta_{0-4}$ are the weights assigned to each accuracy metric that sum to 1. For the current production version, $\beta_{0-4}$ were assigned as 0.4, 0.2, 0.2, 0.1, and 0.1.

@@

Where $\theta$ represents the true cover type of a pixel (field or not field), *D* is the worker's label of that field, and *W$_i$* is an individual worker.  Looking in greater details at this equation, the first half of the righthand side of the equation, P(W$_i$|D), is the "prior" for worker *i* for the current site based on their history of scores from accuracy assessment assignments. The second term, P($\theta$|D, W$_i$), is the probability that the actual class of the pixel in the current assignment is the class that worker *i* says that it is, which is either 0 or 1. There are four possible values for this second term:

@@

Equations \ref{eq:pacc1} and \ref{eq:pacc2} are Producer's accuracies, thus the maximum worker likelihood is equivalent to the worker's average Producer's accuracy.

@@

The other component of equation \ref{eq:prior}, P(W$_i$), is the worker's average score over *m* accuracy assessment assignments:  
\begin{equation} 
\mathrm{P(W_i) \propto \frac{1}{m}\sum_{j=1}^{m}score_j}
\end{equation}

Thus equation \ref{eq:prior} uses two measures of worker accuracy, 1) their overall average accuracy score multipled by 2) their average Producer's accuracy to create a *weight* for their individual maps for the given site. Equation \ref{eq:main} becomes:

@@

$$
Weight_A = score_A * PA_A(field) = P(W_A)P(D=field|W_A) = `r sc[1, 2]` * `r sc[1, 4]` = `r wtA`
$$

@@

```{r labelriskhist, echo = FALSE, out.width="40%", fig.cap="The distribution of Bayesian Risk values for training (left column) and validation (right column) sites in each AOI, with the average value indicated by vertical lines. The first three rows (panel titles beginning with 'Cl') indicate distributions of Bayes Risk in the initial training clusters, including the first ('Cl2a') and second ('Cl2b') mappings of Cluster 2.", fig.align='center', message=FALSE, results='hold'}
knitr::include_graphics('figures/si_label_risk_hists.png')
```
